CUNY SPSS Data Science Math Homework 1

### 2018-07-19 data-science-math/Homework 1.Rmd
More work

>>>>

### Question 21
Inventory cost is defined as the cost of holding stock and the cost of ordering.  The inventory cost as a function of the iron lot size is:

$$C(i)=\frac{120}{i}(6+4.5(i))+(1.60\frac{i}{2})$$
This function assumes the irons are selling at a constant rate (no seasonality) throughout the year.  Simplifing the function:

$$C(i)=\frac{620}{i}+ \frac{540i}{i}+(0.8i) = \frac{620}{i}+0.8i+540$$

Since we want to minimize this cost we take the first derivative and set it equal to zero.

$$C'(i)=-\frac{720}{i^2} +0.8$$

$$0=-\frac{720}{i^2} +0.8$$
$$\frac{720}{i^2}=0.8$$
$$720=0.8i^2$$
$$i^2=\frac{720}{0.8}=900$$
$$i=\sqrt{900}=30$$
So the **lot size is 30 irons**.  Since we are expecting to sell 120 irons per year this would require **4 orders**.

### Question 22

$$Volume = 18432ft^2 = x\cdot x \cdot y \Rightarrow y=\frac{18432}{x^2}$$
The cost is the sum of the sides, top and bottom.  The sides and top material cost $3.00 per square foot and the bottom is $5.00.

$$C(x,y) = 3(4xy) + 3x^2 + 5x^2 = 12xy+8x^2$$
Substituting in y:
$$ C(x)=\frac{12x\cdot 18432}{x^2}+8x^2=\frac{221184}{x}+8x^2$$
Minimize the cost function:
$$ C'(x)=-\frac{221184}{x^2}+16x$$
$$ 0=-\frac{221184}{x^2}+16x\Rightarrow 0=-221184+16x^3 \Rightarrow 0=-13824 + x^3 $$
$$ x^3 = 13824 \Rightarrow x=\sqrt[3]{13824} = 24$$
Plugging 24 into the volume equation and solving for y:
$$18432 = x^2y\Rightarrow 18432=(24)^2 y\Rightarrow 18432=576 y \Rightarrow y=\frac{18432}{576} \Rightarrow y = 32$$
Now checking everything with R:
```{r}
f22 <- function(x){
  (3*(4*x*(18432/(x**2)))) + (3*x**2) + (5*x**2)
}
f22_prime <- Deriv(f22)
library(rootSolve)
x22 <- uniroot.all(f22_prime, c(0,100))
x22
y22 <- function(x){18432/(x**2)}
y22(x22)
```

### Question 23

### Question 24

### Question 25

### Question 26

### Question 27

### Question 28

### Question 29

******
### Question 30

$$ \int_{-7}^2 x\sqrt{x+7}dx$$

For this problem $u=x$ and $dv=\sqrt{x+7}dx$.  Calculate $du$ and $v$:

$du=1dx$ and $v = \int \sqrt{x+7}dx = \frac{2}{3}(x+7)^\frac{3}{2}$

Plugging it into the integration by parts formula:

$$ \int_a^b udv = uv]_a^b -\int_a^b vdu$$

$$ \int_{-7}^2x\sqrt{x+7}dx]_{-7}^2 -\int_{-7}^2 \frac{2}{3}(x+7)^\frac{3}{2}\cdot 1dx$$
Integrate the right hand side

$$ \frac{2x}{3}(x+7)^\frac{3}{2}]_{-7}^2 -\frac{4}{15}(x+7)^\frac{5}{2}]_{-7}^2 $$

Plugging in the -7 and 2 yeilds -28.8 as shown below:
```{r}
f30 <- function(a, b){
  left <- function(x){
    ((2*x)/3)*(x+7)**(3/2)
  }
  right <- function(y){
    (4/15)*(y+7)**(5/2)
  }
  (left(b)-left(a))-(right(b)-right(a))
}

f30(-7,2)
```
******

### Question 31

#### Step 1
In the interest of time I will solve this question by building a simple model
```{r}
bounce <- function(total_times, drop_height, debug=F){
  rebound = .22 # Amount of the rebound as a share of drop height
  times_ball_hit_the_ground = 1
  total_distance = drop_height
  if(debug){
    message(paste(total_distance, 'meters after ball hits the ground',times_ball_hit_the_ground,'times'))
  }
  while(times_ball_hit_the_ground < total_times){
    drop_height = rebound * drop_height 
    total_distance = total_distance + (2 * drop_height) #going Up and down
    times_ball_hit_the_ground = times_ball_hit_the_ground + 1
    if(debug){message(paste(total_distance, 'meters after ball hits the ground',times_ball_hit_the_ground,'times'))}
  }
  if(!debug){
  message(paste(total_distance, 'meters after ball hits the ground',times_ball_hit_the_ground,'times'))
  }
}

bounce(20, 46, T)
```
So the ball traveled 71.94872 meters when it hit the ground on the 20th time.  I would note that the additional distance is very small after the 7th

#### Step 2
To evaluate the total distance as the number of bounces heads to infinity I will cheat and plug in a really large number and see what it tends toward.
```{r}
bounce(1000000, 46)
```

So it is tending toward 72 meters.

### Question 34
